Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-16 manuscript.qmd
setup pipeline with 3 LNLs

```{python}
#| echo: false

@@

Below we compare the predicted with the observed prevalence of some involvement patterns.

@@

```{python}
#| echo: false
#| label: tbl-midline-params
#| tbl-cap: Mean sampled parameter estimates of the midline model and the respective standard deviation.
model = shared.get_model(which="midline", load_samples=True)
samples = shared.get_samples(which="midline")

names = list(model.get_params().keys())
means, stds = samples.mean(axis=0), samples.std(axis=0)

@@

params_table = pd.DataFrame({"name": names, "mean": means, "std": stds})
(
  params_table.style
  .format("{:.2%}", subset=["mean", "std"])
  .apply(right_align, subset=["mean", "std"])
  .hide()
)
```

>>>>

```{python}
#| echo: false
import re

@@

First, we look at the prevalence of contralateral involvement for the LNLs II, III, and IV. This is plotted in @fig-prevalences, both for early and advanced T-category.

- [ ] Run sampling for all LNLs
- [ ] compute prevalences for set of interesting scenarios

@@

```{python}
#| echo: false
#| label: tbl-midline-params
#| tbl-cap: Mean sampled parameter estimates of the midline model and the respective standard deviation.
def map_param_names(name: str) -> str:
  """Make parameter names more readable."""
  try:
    return {
      "midext_prob": "Mid. ext. probability",
      "mixing": "Mixing ⍺",
      "late_p": "late T-cat. binom. prob.",
    }[name]
  except KeyError:
    return re.sub(
      r"(ipsi|contra)_", r"\g<1>: ", name
    ).replace(
      "to", " ➜ "
    ).replace(
      "_spread", ""
    )

model = shared.get_model(which="midline", load_samples=True)
samples = shared.get_samples(which="midline")

names = [map_param_names(p) for p in model.get_params()]
means, stds = samples.mean(axis=0), samples.std(axis=0)

@@

params_table = pd.DataFrame({"Parameter": names, "Mean": means, "Std. Dev.": stds})
(
  params_table.style
  .format("{:.2%}", subset=["Mean"])
  .format("± {:.2%}", subset=["Std. Dev."])
  .apply(right_align, subset=["Mean", "Std. Dev."])
  .hide()
)
```
